Embedded Scalars: {A}n Experimental Revisit

### 2014-05-15 text/paper/paper4.tex
reworked introduction

\usepackage{amsmath}            % Formeln
\usepackage{amsfonts}           % Fonts for Formulas
\usepackage{amssymb}
\usepackage[final]{graphicx}
\usepackage{booktabs}
\usepackage{enumerate}
\usepackage{lipsum}
\usepackage{txfonts} % for strict implication symbols
\usepackage{soul}
\usepackage{relsize} % provides command \relsize{+/-x} for relative
                     % font size changes
\usepackage[german,english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc} 
\usepackage{subfig}
\usepackage{xypic}
\usepackage{url}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,automata,backgrounds,petri,fit,decorations.pathmorphing}
\usepackage{refcount}
\usepackage{xspace} % for \xspace in definition of acronyms etc.
\usepackage{attrib} % for right-aligned references at the end of
                    % quotes; part of Frankenstein bundle, but 
\renewcommand\PreTrib {}   % overwrite these commands, from attrib.sty
\renewcommand\PostTrib {}  % to suppress additional brackets around
                           % attributions
\usepackage{eurosym}
\usepackage{pgfplots}

@@

@@

\begin{abstract}
  Scalar item \emph{some} is widely assumed to undergo, given relevant
  preconditions, a pragmatic meaning enrichment to \emph{some but not
    all} if it occurs in matrix position. The question under which
  circumstances this meaning enrichment can take place in embedded
  position plays an important role in deciding how to delineate
  semantics and pragmatics. % Some claim
  % that it requires marked intonation for the relevant pragmatic
  % enrichment to occur in embedded position; others allow for it more
  % freely.
  We present a novel experimental paradigm to test whether the
  relevant pragmatic enrichment is available in embedded positions
  with or without prosodic markedness. On top of adding prosodic
  manipulation, our experimental design was catered to a number of
  methodological difficulties that were identified for previous
  related studies. The data obtained refutes both a traditional
  Gricean view of scalar implicature calculation, as well as the more
  recent grammatical approach.
\end{abstract}

@@

The existential quantifier \emph{some} is usually assumed to receive a
semantic interpretation similar to logical $\exists$, so that the
sentence \emph{Some boys cried} is literally true in a situation where
all boys cried. But it is also usually considered to be a
\mymark{scalar item} in that its use invites comparison with (at
least) the semantically stronger universal quantifier \emph{all}
\citep[c.f.][]{Horn1972:On-the-Semantic,Gazdar1979:Pragmatics:-Imp,AtlasLevinson1981}. This
comparison can lead to an upper-bounding meaning enrichment, e.g.,
when an utterance of (\ref{bsp:Plain-SI-Target}) is taken to invite
the inference in (\ref{bsp:Plain-SI-Implicature}).

@@

% If this upper-bounding inference would occur often and
% systematically enough, then it may well be that also embedded
% occurrences of \emph{some} get enriched, in some fashion or other, to
% contribute the enriched meaning \emph{some but not all} also under the
% scope of other logical operators.
% Indeed, even
% \citeauthor{Grice1975:Logic-and-Conve} envisaged this possibility when
% he wrote: ``It may not be impossible for what starts life, so to
% speak, as a conversational implicature to become conventionalized''
% \citep[p.58]{Grice1975:Logic-and-Conve}.

This paper deals with the interpretation of two types of sentences,
where the scalar item \emph{some} occurs in the scope of other logical
operators. In \as-sentences (mnemonic for \textit{all \dots some \dots})
as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded under
universal quantifier \emph{all}. In \es-sentences (mnemonic for
\textit{exactly one \dots some \dots}) like (\ref{bsp:GE}) \emph{some}
takes scope under the non-monotonic quantifier \emph{exactly one}.
According to current pragmatic theory, there are at least three
relevant candidate readings for \as- and \es-sentences: (i) a
\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
(\ref{bsp:GE-Global}) where, according to Gricean intuition, we enrich
utterances of (\ref{bsp:AE}) and (\ref{bsp:GE}) with the negation of
alternative utterances of the corresponding sentences
(\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
\emph{some} is replaced by \emph{all}; and also (iii) a \emph{local
  reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
\emph{some} is interpreted as \emph{some but not all} in the scope of
the embedding quantifier.

@@

\noindent Given this relative abundance of theoretically conceivable
readings, two interlocked empirical questions arise:
\begin{enumerate}[Q1:]
\item which of these readings are available to na\"{i}ve subjects; and
\item which of the available readings are preferred.\fn{It may
    ultimately be impossible to keep unavailability and strong
    dispreference strictly apart. For our purposes this is not
    important. Every time we speak of availability, the so-inclined
    reader may think of non-negligible preference.}
\end{enumerate}
Addressing these questions empirically is relevant because they lie at
the heart of the current debate about the exact location and nature of
the interface between semantics and pragmatics. The controversy
concerns the question under which circumstances and to what extent the
upper-bounding inference from \emph{some} to \emph{some but not all}
can occur within the compositional computation of semantic values. Two
opposing theoretical positions can be distinguished here:
\emph{traditionalism} holds in particular that local readings should
not be readily attested unless marked by special intonation;
\emph{grammaticalism} holds that local readings are available and
indeed preferred. To distinguish between these opposing positions, it
is particularly relevant to assess the availability and relative
preference of local readings for \as- and
\es-sentences. %(Section~\ref{sec:theories-predictions}
%will discuss the relevant theoretical positions and the significance
%of alleged local readings in more detail.)

% Firstly, there are \mymark{pragmatic traditionalists} who seek to
% conserve the spirit of \citeauthor{Grice1975:Logic-and-Conve}'s
% (\citeyear{Grice1975:Logic-and-Conve}) original ideas as much as
% possible
% \citep[e.g.][]{Spector2006:Scalar-Implicat,Sauerland2004:Scalar-Implicat,Russell2006:Against-Grammat,vanRooijSchulz:ExhaustiveInterpretation,Geurts2010:Quantity-Implic,Franke2011:Quantity-Implic}. Traditionalists
% acknowledge the existence of global readings, but might consider local
% readings either unavailable or a beast distinct from scalar
% implicatures. An often phrased intuition of the traditionalists is
% that local readings, since they are special kinds of inferences,
% require special intonation, in particular emphatic stress on the
% scalar item.

% Opposed to that is the camp of \mymark{lexical conventionalists}
% \citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}
% who maintain that scalar \emph{some} is lexically ambiguous between
% the standard logical meaning \emph{some and maybe all} and the
% upper-bounded meaning \emph{some but not all}. As the latter is
% considered a default, lexical conventionalism has no problem
% accounting for local readings, and in fact would consider these the
% preferred readings.

% Thirdly and finally, there is the camp of \mymark{grammaticalists} who
% defend that the distribution of upper-bounded readings of \emph{some}
% is best explained by postulating a silent operator, akin to the
% meaning of the particle \emph{only}
% \citep{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}. According
% to the grammatical view, this silent operator may be applied in
% compositional semantics also in the scope of other logical operators,
% but, so as not to overgenerate readings, the availability of readings
% is constraint by the \emph{strongest meaning hypothesis}
% \citep{DalrympleKanazawa1998:Reciprocal-Expr}. Grammaticalist theories
% predict that all three types of readings are available. Moreover,
% according to the grammatical view, the local reading is preferred for
% \as-sentences, while the global one is preferred for
% \es-sentences. (More precisely, as we will see
% Section~\ref{sec:theories-predictions}, depending on the variant of
% the strongest meaning hypothesis employed, either the global reading
% is predicted to be preferred for \es-sentences, or the global and the
% local reading are predicted to be equally preferred.)

A number of empirical studies have already targeted this issue
\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. Unfortunately,
results from these studies do not provide as clear-cut evidence for or
against either of the two rivaling positions as one would hope
for. This is due to several reasons. Firstly, previous studies have
only accumulated limited evidence pertaining to the preference
relations between putative readings of both types of
sentences. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue, the putative
evidence for the availability of local readings of \as-sentences
suggested by studies of \citet{CliftonDube2010:Embedded-Implic} and
\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounds
with what van Tiel and Geurts call \emph{typicality effects}. Finally,
and most importantly, previous studies presented target sentences
visually. This is highly problematic, because traditionalists admit to
the availability of local readings as long as it is intonationally
marked
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}. We
will address this extant position as the \emph{intonational markedness
  hypothesis}. But if intonation plays a role, it is absolutely vital
to present target sentences auditorily, so as to be able to control
for effects of ``silent prosody'' that subjects may apply when reading
a sentence \citep[see][]{Bader98,Fodor98}.

This paper therefore presents results form an experimental study
designed to deal with the above mentioned problems. We presented
sentence material auditorily and explicitly manipulated intonational
stress on embedded scalar items. To cater for potential pictorial
confounds, such as from typicality, we employed an \emph{incremental
  verification task} in which parts of a to-be-evaluated picture were
hidden and only revealed piece-wise at the participants' request until
they felt able to give a binary truth-value judgement
\citep[see][]{Conroy2008}. This way we obtained categorical behavioral
data that is both indicative of the reading subjects assumed and
independent of any potential pictorial confounds. We also made sure
that our method is able to reveal information about reading
preferences by including a control condition with ambiguous sentences
with a well-known preference on available readings.

The data obtained by this method contradicts both traditionalism and
grammaticalism. Contrary to traditionalism and the intonational
markedness hypothesis, we found evidence for local readings for both
kinds of critical sentences, irrespective of intonational stress. Even
the intonational markedness hypothesis on its own is not supported by
our data: stress on embedded scalar items did not lead to an increase
in answers suggesting a local reading. But also grammaticalism is
incongruent with the observed pattern in our data.  Grammaticalism
predicts local readings to be the preferred readings, but we found no
evidence for that. More strongly even, the preference order among
putative readings suggested by our data cannot even in principle be
explained by the general kind of second-order selection criterion that
is currently favored by grammaticalists, namely by comparison of
logical strength of putative readings
\citep[e.g.][]{ChierchiaFox2008:The-Grammatical}. In sum, our data
sheds doubt on both traditionalism and grammaticalism in their
currently most common forms. We conclude the paper by some speculation
about how either position might be amended in the light of our data.

The paper is structured as follows. Section~\ref{sec:get-know-your}
elaborates on the three kinds of relevant readings for our target
sentences. Section~\ref{sec:theories-predictions} works out the
predictions of traditionalism and grammaticalism about availability
and preference of readings of our target
sentences. Section~\ref{sec:previous-studies} recaps the results of
related experimental studies to the extent necessary to motivate our
own approach. Section~\ref{sec:exp} eventually contributes our
experimental design and our results.

@@

It is worth noting that an alternative theory of scalar implicature
explains the observed preference ordering
(\ref{bsp:observed-preferences}) in a completely straightforward
manner.  \emph{Conventionalism} (also sometimes called
\emph{lexicalism}) proposes that if the upper-bounding inference from
\emph{some} to \emph{some but not all} occurs frequently, it would be
inefficient to execute over and over again the Gricean reasoning that
traditionalists propose
\citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}. Conventionalism
therefore assumes that scalar inferences have become routinized,
hard-wired, so much so that there are two lexical entries for a scalar
item like \emph{some}, one with logical meaning \emph{some and maybe
  all} and one with the upper-bounded meaning \emph{some but not
  all}. \citet{LevinsonPresumptiveMeanings2000} proposed that the
latter is the preferred default meaning, a position which has
therefore ofttimes be addressed as \mymark{defaultism}. Unfortunately,
defaultism has strong empirical evidence against it, because several
processing studies show that the computation of scalar inferences
appears to be time- and effort-consuming, when they do arise, not when
they do not
\citep[see][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
there is also competing evidence that scalar inferences are available
in immediate, low-level processes, such as the resolution of
referential expressions in a visual-world paradigm
\citep{GrodnerKlein2010:Some-and-Possib}. For our purposes, it is
interesting to note that the preference relation in
(\ref{bsp:observed-preferences}) is predicted by the dual of
defaultism, which has not been defended in the literature as far as we
know, which posits a lexical ambiguity but predicts that the logical
meanings are \emph{ceteris paribus} preferred over the upper-bounded
meanings.

@@

\noindent In the context of the present study, this would then be good
news for traditionalism, because a combined
traditionalism+conventionalism would predict the observed data
well. The combined position would even be able to explain something
that grammaticalism cannot make sense of as easily, namely the
observation that there were rather consistent localists among the
participants of our study. The combined tradionalism+conventionalism
could explain this by the assumption that some (lazy?, smart?)
speakers have made a conventionalized upper-bounding meaning entry for
scalar \emph{some} while others keep computing things on the fly. It
is not clear how grammaticalism can account for the intra-subjective
consistency. Still, this is not an argument \emph{for} traditionalism,
because the point remains that traditionalism as such fails to predict
the observed data.

>>>>

\usepackage{amsmath}            % Formeln
\usepackage{amsfonts}           % Fonts for Formulas
\usepackage{amssymb}
\usepackage[final]{graphicx}
\usepackage{booktabs}
\usepackage{enumerate}
\usepackage{lipsum}
\usepackage{txfonts} % for strict implication symbols
\usepackage{soul}
\usepackage{relsize} % provides command \relsize{+/-x} for relative
                     % font size changes
\usepackage[german,english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc} 
\usepackage{subfig}
\usepackage{xypic}
\usepackage{url}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,automata,backgrounds,petri,fit,decorations.pathmorphing}
\usepackage{refcount}
\usepackage{xspace} % for \xspace in definition of acronyms etc.
\usepackage{attrib} % for right-aligned references at the end of
                    % quotes; part of Frankenstein bundle, but 
\renewcommand\PreTrib {}   % overwrite these commands, from attrib.sty
\renewcommand\PostTrib {}  % to suppress additional brackets around
                           % attributions
\usepackage{eurosym}
\usepackage{pgfplots}
\usepackage{todonotes}

@@

\renewcommand{\mymark}[1]{\textbf{#1}}

@@

\begin{abstract}
  Scalar item \emph{some} is widely assumed to receive a pragmatic
  meaning enrichment to \emph{some but not all} if it occurs in matrix
  position. The question under which circumstances this enrichment can
  occur in certain embedded positions plays an important role in
  deciding how to delineate semantics and pragmatics. % Some claim
  % that it requires marked intonation for the relevant pragmatic
  % enrichment to occur in embedded position; others allow for it more
  % freely.
  We present new experimental data that bears on this theoretical
  issue. In distinction to previous experimental approaches, we
  presented sentence material auditorily in order to explicitly
  control prosodic markedness of the scalar item. Moreover, our
  experimental design gives insight into the preference of
  hypothesized meaning differences, not only on their general
  availability. The data obtained in this way turns out problematic
  for both a traditional Gricean view of scalar implicature
  calculation, as well as the more recent grammatical approach.
\end{abstract}

@@

The existential quantifier \emph{some} is usually assumed to receive a
semantic interpretation similar to logical $\exists$, so that
(\ref{bsp:Plain-SI-Target}) is literally true even when Hans solved
all of the problems. But it is also usually considered to invite
comparison with (at least) the semantically stronger universal
quantifier \emph{all}
\citep[c.f.][]{Horn1972:On-the-Semantic,Gazdar1979:Pragmatics:-Imp,AtlasLevinson1981}. This
scalar comparison can lead to an upper-bound meaning enrichment, e.g.,
when an utterance of (\ref{bsp:Plain-SI-Target}) is taken to invite
the inference in (\ref{bsp:Plain-SI-Implicature}).

@@

% If this upper-bound inference would occur often and
% systematically enough, then it may well be that also embedded
% occurrences of \emph{some} get enriched, in some fashion or other, to
% contribute the enriched meaning \emph{some but not all} also under the
% scope of other logical operators.
% Indeed, even
% \citeauthor{Grice1975:Logic-and-Conve} envisaged this possibility when
% he wrote: ``It may not be impossible for what starts life, so to
% speak, as a conversational implicature to become conventionalized''
% \citep[p.58]{Grice1975:Logic-and-Conve}.

This paper deals with the interpretation of two types of sentences,
where the scalar item \emph{some} occurs in the scope of other logical
operators. In \as-sentences (mnemonic for \textit{all \dots some
  \dots}) as in (\ref{bsp:AE}) the scalar item \emph{some} is embedded
under universal quantifier \emph{all}. In \es-sentences (mnemonic for
\textit{exactly one \dots some \dots}) like (\ref{bsp:GE}) \emph{some}
takes scope under the non-monotonic quantifier \emph{exactly one}.
According to current pragmatic theory, there are at least three
relevant candidate readings for \as- and \es-sentences: (i) a
\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
(\ref{bsp:GE-Global}) where we enrich the meaning of (\ref{bsp:AE})
and (\ref{bsp:GE}) with the negation of the corresponding sentences
(\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
\emph{some} is replaced by \emph{all}; and also (iii) a \emph{local
  reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
\emph{some} is interpreted as \emph{some but not all} in the scope of
the embedding quantifier.

@@

\noindent Given this plurality of hypothesized readings, we need to
ask:
\begin{enumerate}[Q1:]
\item which of these readings are available to na\"{i}ve subjects; and
\item which of the available readings are preferred.\fn{It may
    ultimately be impossible to keep unavailability and strong
    dispreference strictly apart. For our purposes this is not
    important. Every time we speak of availability, the so-inclined
    reader may think of non-negligible preference.}
\end{enumerate}
Addressing these questions empirically is relevant because they lie at
the heart of the current debate about the exact location and nature of
the interface between semantics and pragmatics. The controversy
concerns the question under which circumstances and to what extent the
upper-bound inference from \emph{some} to \emph{some but not all} can
occur within the compositional computation of semantic values. Two
opposing theoretical positions can be distinguished here:
\emph{traditionalism} holds in particular that local readings should
not be readily attested unless marked by special intonation;
\emph{grammaticalism} holds that local readings are available and, at
least under the most prominent of selection principles for candidate
readings, even preferred (see Section~\ref{sec:grammaticalism}). To
distinguish between these opposing positions, it is therefore
necessary to assess the availability and relative preference of
readings for \as- and \es-sentences under conditions that control for
intonational markedness. This is what this paper aims to do.

A number of empirical studies have already studied sentences like
(\ref{bsp:AE}) and (\ref{bsp:GE}) this issue
\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. Unfortunately,
results from these studies do not provide uncontroversial evidence to
decide between the two main rivaling positions. This is due to several
reasons. Firstly, previous studies have only accumulated limited
evidence pertaining to the preference relations between putative
readings of both types of sentences. Secondly, as
\citet{Tielvan-Tiel2012:Embedded-Scalar} and
\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue, the putative
evidence for the availability of local readings of \as-sentences
suggested by studies of \citet{CliftonDube2010:Embedded-Implic} and
\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounds
with what van Tiel and Geurts call \emph{typicality effects}. Finally,
and most importantly, previous studies presented target sentences
visually. This is highly problematic, because traditionalists admit to
the availability of local readings as long as it is intonationally
marked
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}. We
will address this extant position as the \emph{intonational markedness
  hypothesis}. But if intonation plays a role, it is vital to present
target sentences auditorily, so as to be able to control for effects
of ``silent prosody'' that subjects may apply when reading a sentence
\citep[see][]{Bader98,Fodor98}.

This paper therefore presents results form an experimental study
designed to deal with the above mentioned problems. We presented
sentence material auditorily and explicitly manipulated intonational
stress on embedded scalar items. To cater for potential pictorial
confounds, such as from typicality, we employed an \emph{incremental
  verification task} in which parts of a to-be-evaluated picture were
hidden and only revealed piece-wise at the participants' request until
they felt able to give a binary truth-value judgement
\citep[see][]{Conroy2008}. This way we obtained categorical behavioral
data that is both clearly indicative of the reading that subjects
assumed and fairly independent of any potential pictorial
confounds. Moreover, this method also gives information about reading
preferences. We validated this by including a control condition with
ambiguous sentences with a well-known preference on available
readings.

The data obtained by this method is problematic for both
traditionalism and grammaticalism. Contrary to traditionalism and the
intonational markedness hypothesis, we found evidence for local
readings for both kinds of critical sentences, irrespective of
intonational stress. \todo{enlarge: how big was this effect? can
  traditionalists explain this away?} But also grammaticalism is
incongruent with the observed pattern in our data. Backed up by the
Strongest Meaning Hypothesis
\citep{DalrympleKanazawa1998:Reciprocal-Expr}, grammaticalism predicts
local readings to be the preferred readings, but we found no evidence
for that. More strongly even, the preference order among putative
readings suggested by our data cannot even in principle be explained
by comparisons of logical strength among putative readings. In sum,
our data sheds doubt on both traditionalism and grammaticalism in
their currently most common forms. We conclude the paper by some
speculation about how either position might be amended in the light of
our data.

The paper is structured as follows. Section~\ref{sec:get-know-your}
elaborates on the three kinds of relevant readings for our target
sentences. Section~\ref{sec:theories-predictions} works out the
predictions of traditionalism and grammaticalism about availability
and preference of readings for these
sentences. Section~\ref{sec:previous-studies} reviews related
experimental studies to the extent necessary to motivate our own
approach. Section~\ref{sec:exp} eventually contributes our
experimental design and our results.

@@

It is worth noting that an alternative theory of scalar implicature
explains the observed preference ordering
(\ref{bsp:observed-preferences}) in a completely straightforward
manner.  \emph{Conventionalism} (also sometimes called
\emph{lexicalism}) proposes that if the upper-bound inference from
\emph{some} to \emph{some but not all} occurs frequently, it would be
inefficient to execute over and over again the Gricean reasoning that
traditionalists propose
\citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}. Conventionalism
therefore assumes that scalar inferences have become routinized,
hard-wired, so much so that there are two lexical entries for a scalar
item like \emph{some}, one with logical meaning \emph{some and maybe
  all} and one with the upper-bounded meaning \emph{some but not
  all}. \citet{LevinsonPresumptiveMeanings2000} proposed that the
latter is the preferred default meaning, a position which has
therefore ofttimes be addressed as \mymark{defaultism}. Unfortunately,
defaultism has strong empirical evidence against it, because several
processing studies show that the computation of scalar inferences
appears to be time- and effort-consuming, when they do arise, not when
they do not
\citep[see][]{BrehenyKatsos2006:Are-Generalised,BrehenyKatsos2008:Experimental-In,NeysDe-NeysSchaeken2007:When-People-Are}. But
there is also competing evidence that scalar inferences are available
in immediate, low-level processes, such as the resolution of
referential expressions in a visual-world paradigm
\citep{GrodnerKlein2010:Some-and-Possib}. For our purposes, it is
interesting to note that the preference relation in
(\ref{bsp:observed-preferences}) is predicted by the dual of
defaultism, which has not been defended in the literature as far as we
know, which posits a lexical ambiguity but predicts that the logical
meanings are \emph{ceteris paribus} preferred over the upper-bounded
meanings.

@@

\noindent In the context of the present study, this would then be good
news for traditionalism, because a combined
traditionalism+conventionalism would predict the observed data
well. The combined position would even be able to explain something
that grammaticalism cannot make sense of as easily, namely the
observation that there were rather consistent localists among the
participants of our study. The combined tradionalism+conventionalism
could explain this by the assumption that some (lazy?, smart?)
speakers have made a conventionalized upper-bound meaning entry for
scalar \emph{some} while others keep computing things on the fly. It
is not clear how grammaticalism can account for the intra-subjective
consistency. Still, this is not an argument \emph{for} traditionalism,
because the point remains that traditionalism as such fails to predict
the observed data.
